|

### 2022-03-27 08-Discussion.Rmd
Add "and meta-analysis" to description of the systematic review

In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes. The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.

>>>>

In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review [and meta-analyses]{.correction}
 of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes. The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
